Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support)

### 2017-02-14 csf-2017/paper.tex
First attempt at an abstract

\begin{abstract}
  abc
\end{abstract}

>>>>

\begin{abstract}  
  Capability machines provide security guarantees at machine level
  which makes them an interesting target for compilation schemes that aim to
  provably enforce control-flow integrity, encapsulation of local
  state, and such properties.
  We provide a formalisation of a representative capability machine
  and propose a novel stack management discipline for enforcing
  control-flow integrity and encapsulation of local state on it. To prove
  these properties, we provide a logical relation that semantically
  captures capability safety. The capability safety defined by the
  logical relation goes beyond the
  proposed stack management discipline and can be used to reason about
  any capability safe program.
\end{abstract}
